Data Raw Files

### 2020-06-12 data-raw/README.Rmd
Clean up README for data-raw directory

Two files in this directory detail the pre-processing of disease data, [import_and_preprocess.md](import_and_preprocess.md) and an R script, [IRRI_weather_data.R](IRRI_weather_data.R) that imports weather data for 2015 and 2016 and runs statistical checks to ensure that the dry seasons in each year are not statistically different.

>>>>

One file exists in this directory, [IRRI_weather_data.R](IRRI_weather_data.R).
It imports weather data for 2015 and 2016 and runs statistical checks to ensure that the dry seasons in each year are not statistically different.
They were not.
